---
title: "Prediction of A Diamond Price"
author: "Ula Jiang"
date: "16 May 2018"
output: ioslides_presentation
---

## Executive Summary
This project is a part of coursera "Developing Data Products" course.  

It shows the informatiom about diamond dataset in UsingR package. The dataset contains 48 observations of diamonds' carat and relative price.


## Functionality
- This app predicts a diamond price when user gives a specific carat.   
- It shows a plot of all the observation data points and the predicted fitted line. 


## Slide with R Output
```{r,include=FALSE}
library(UsingR)
data("diamond")
```
```{r, comment=""}
head(diamond,10)
```


## Plot of observations and fitted line
```{r, echo=FALSE}
model <- lm(price ~ carat, data = diamond)
modelPred <- predict(model, newdata = data.frame(carat = diamond$carat))
plot(diamond$carat, diamond$price, 
         xlab = "Carat of a Diamond",
         ylab = "Price (in dollar $)", 
         xlim = c(0.10, 0.40),
         ylim = c(100, 1250))
abline(model, col = "red", lwd = 2)
```

